A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-01 07_Manuscript.Rmd
Commence Results section

>>>>

Overall the meta-analysis indicated that, with the exception of `Early` single sprays all the the spray schedules were effective at protecting mungbean yields, relative to the no spray controls (Figure 1). 
Treatments which incorporated multiple fungicide applications, `recommendedPlus` and `LatePlus` produced the highest yield protection estimates at 196 and 220 kg / ha respectively (Table 3). 
Both `RecommendedPlus` and `LatePlus` were also significantly higher than single applications starting `Early` (P = 0.008 and P = 0.003 respectively) and `Late`(P = 0.05 and P = 0.03 respectively). 
Within the single fungicide application treatments `recommended` provided the highest yield protection, and was estimated at saving an average of 160 kg / ha relative to the no spray control (P < 0.0001). `recommended` treatments were was also significantly higher than `Early` treatments by 122 kg / ha (P = 0.004).

The $Q_M$ omnibus test of moderators, shows the moderators significantly influence the model ($Q_M = 26.22, df = 5, p < 0.0001$) and we can reject the null hypothesis ($H_0 : \beta_1 = \beta_2 = \beta_3 =\beta_4 = 0$) that there is no difference between the moderators [@Viechtbauer2010].
The analysis shows there is still a significant amount of residual heterogeneity ($Q_E = 568.31, df = 111, p < 0.0001$) not captured by the spray management moderator indicating other possible moderators which might influence grain yield.

A log-ratio test, based on a chi-squared distribution, indicated that retaining the SpraySchedule variable as a random interactive term provided a significantly better model (P = 0.0179).

```{r table3_Contrasts}
T3 <- read.csv(here("cache/Table3_contrasts.csv"), stringsAsFactors = FALSE)
T3 %>%
   kable()

```
